An IFS study of Low-powered Radio Galaxies

### 2018-01-29 paper.tex
Added in Acknowlegements
 On branch master
 Changes to be committed:
	modified:   paper.tex

\section*{Acknowledgements}

>>>>

\section*{Acknowledgements}
JW acknowledges funding from the Science and Technology Facilities Council Grant Code 1577871. This research makes extensive use of observation from VIMOS \citep{LeFevre2003} and archival data from MUSE \citep{Bacon2010}. We also make use of observations from the APEX \citep{Gusten2006} and the ALMA. ALMA is a partnership of ESO (representing its member states), the National Science Foundation (NSF; USA) and the National Institutes of Natural Sciences (NINS; Japan), together with the National Research Council (NRC; Canada), the Ministry of Science and Technology (MOST; Taiwan) and Academia Sinica Institute of Astronomy and Astrophysics (ASIAA; Taiwan), and Korea Astronomy and Space Science Institute (KASI; Republic of Korea), in cooperation with the Republic of Chile. The Joint ALMA Observatory is operated by ESO, Associated Universities Inc./National Radio Astronomy Observatory (AUI/NRAO; USA) and National Astronomical Observatory of Japan (NAOJ). We also make use of data products from the 2MASS, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center (IPAC)/California Institute of Technology, funded by the National Aeronautics and Space Administration (NASA) and NSF. We also make use of the Set of Identifications, Measurements and Bibliography for astronomical Data (SIMBAD) database and Portal tool, operated at the Strasbourg astronomical Data Centre (CDS), France. This research has made use of the following resources and programs: arXiv.org; the Astrophysics Data System (ADS); \textsc{astropy}, a community-developed core \textsc{python} package for astronomy \citep{TheAstropyCollaboration2013}; \textsc{kinemetry} \citep{Krajnovic2006}; \textsc{ipython} \citep{Perez2007}; \textsc{matplotlib} \citep{Hunter2007}; \textsc{p3d} \citep{Sandin2010, Sandin2011}; \textsc{pPXF} \citep{Cappellari2004}; \textsc{py3d} \citep{Sanchez2011, Husemann2013, Husemann2014}; \textsc{scipy} \citep{Oliphant2007, Millman2011}; \textsc{numpy} \citep{VanderWalt2011}; \textsc{spectools} (Ryan Houghton and Simon Zieleniewski, private comm.); and \textsc{voronoi\_2d\_binning} \citep[including the SAURON colourmaps; ][]{Cappellari2003}.
